Intensity Modulated Radiation Therapy using Tomotherapy

### 2014-12-02 BME 560/Paper.tex
Updates..

  \subsection{Construction}
  \begin{figure}
    \centering
    \subfloat[\label{fig4a}][A simplified view of the Helical Tomotherapy 
    treatment head system in use today. The setup consists of a 6 MV linac to 
    produce an x-ray beam which is collimated down to a fan-beam using 2 
    moveable jaws (denoted as `y-jaws' in the image)]{
      \includegraphics[width=\linewidth]{fig4}}\\
    \subfloat[][]{
      \includegraphics[width=\linewidth]{fig5}}

  \end{figure}
  \label{construction}
  \subsubsection{A note on Serial Tomotherapy}
  \subsection{Radiation Characteristics}
  \label{radiation}
  \subsection{Comparisions between IMRT techniques}
  \label{comparisions}
    \begin{table*}[htbp!]
      \centering
      \caption{A comparision between standard and non-standard IMRT delivery 
      systems (Ref. \cite{Fenwick2006})}
      \small{
      \begin{tabulary}{\linewidth}{LLLLLLL}
        \toprule[0.04cm]

>>>>

  \subsection{Construction}
  \label{construction}
  \begin{figure}
    \centering
    \subfloat[][]{
      \includegraphics[width=\linewidth]{fig5}
      \label{fig4a}}\\
    \subfloat[][]{
      \includegraphics[width=\linewidth]{fig4}
      \label{fig4b}}
    \caption{\protect\subref{fig4a} Axial rotation of the fan beam as the 
      patient (represented 
      as a cylinder) traverses laterally (Along the y-axis). 
      \protect\subref{fig4b} A simplified view of the Helical 
      Tomotherapy 
      treatment system (at a gantry angle of 0$^\circ$) in use today. The 
      setup consists of a 6 MV linac to produce an x-ray beam which is 
      collimated down to a fan-beam using 2 moveable jaws (denoted as `y-jaws' 
      in the image). There is also a Binary Multileaf to modulate the beam 
      laterally. \textit{Image  
      courtesy of \cite{Fenwick2004}}}
    \label{fig4}
  \end{figure}
  Figure \ref{fig4} show the basics of dose delivery in the helical tomotherapy 
  system. There is a short in-line 6 MV linear accelerator that rotates on a 
  ring gantry at a source-axis of 85 cms (instead of the usual 100 cms). The 
  patient couch is translated through the gantry bore in the y-direction as 
  shown in \ref{fig4}\protect\subref{fig4a}. The pitch is about 0.2 to 0.5 
  (Pitch is the distance traveled by the couch in one rotation, divided by the 
  field width in the direction of traversal). The pair of y-jaws in 
  \ref{fig4}\protect\subref{fig4b} are used to define the y-width of the beam. 
  These are usually preset to values like 1,2.5, or 5 cm before imaging. 
  Lateral modulation of the beam is achieved using the binary multileaf. This 
  system consists of 64 binary multileaves, each having a width of 6.25 mm 
  projecting onto an isocenter. These leaves transition rapidly between on 
  and off states, the duration of which is made use of to modualate the 
  intensity. 
  \subsubsection{A note on Serial Tomotherapy}
  \subsection{Radiation Characteristics}
  \label{radiation}
  \subsection{Comparisions between IMRT techniques}
  \label{comparisions}
    \begin{table*}[htbp!]
      \centering
      \caption{A comparision between standard and non-standard IMRT delivery 
      systems (Ref. \cite{Fenwick2006})}
      \small{
      \begin{tabulary}{\linewidth}{LLLLLLL}
        \toprule[0.04cm]
